---
title: "Question2"
author: "Hukai Luo"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
abstract:
    In this article, we talk about the solution of queation2. I will show you my way to compute the approximation, how to store the data and how to get the plots.
---

# Question

The approximation of the distribution function of $N(0, 1)$,
\begin{equation}
\Phi(t) = \int_{-\infty}^t \frac{1}{\sqrt{2\pi}} e^{-y^2 / 2} dy,
(\#eq:cdf)
\end{equation}
The Monte Carlo methods:
\begin{equation}
\hat\Phi(t) = \frac{1}{n} \sum_{i=1}^n I(X_i \le t),
\end{equation}
where $X_i$'s are iid $N(0, 1)$ variables.
Experiment with the approximation at $n \in \{10^2, 10^3, 10^4\}$
at $t \in \{0.0, 0.67, 0.84, 1.28, 1.65, 2.32, 2.58, 3.09, 3.72\}$ to form a table.
The table should include the true value for comparison.
Further, repeat the experiment 100 times. Draw box plots of the bias at all $t$.


# Solution

In order to solve this question, I'd like to use function $rnorm()$ to generate random numbers for normal distribution with mean equal to $mean$ and standard deviation equal to $sd$. And then I calculated all the values at $t \in \{0.0, 0.67, 0.84, 1.28, 1.65, 2.32, 2.58, 3.09, 3.72\}$ with the approximation at $n \in \{10^2, 10^3, 10^4\}$.

Following is my source code to calculate the approximation:

```{r code, results='hide'}
t<- c(0.0, 0.67, 0.84, 1.28, 1.65, 2.32, 2.58, 3.09, 3.72)
n<- c(10^2,10^3,10^4)
result<- array(0, c(3,9,100))
for (i in 1:length(n)){
  for(j in 1:length(t)){
    a<- rnorm(n[i],0,1)
    result[i,j,1]<- sum(a<=t[j])/n[i]
  }
}
```
The approximation will be stored in a 3-dimensional array named $result$. And we were required to repeat the experiment 100 times to get the bias at all $t$.
```{r code2, results='hide'}
t<- c(0.0, 0.67, 0.84, 1.28, 1.65, 2.32, 2.58, 3.09, 3.72)
n<- c(10^2,10^3,10^4)
result<- array(0, c(3,9,100))
for (k in 1:100){
  for (i in 1:length(n)){
    for(j in 1:length(t)){
      a<- rnorm(n[i],0,1)
      result[i,j,k]<- sum(a<=t[j])/n[i]
    }
  }
}
```
After that, we draw box plots of the bias at all $t$ in different $n$. In order to get the true value of the the distribution function, I would like to use function $pnorm()$ to generate it.
```{r plots}
True_value<- pnorm(t)
boxplot(result[1,1,]-True_value[1],result[1,2,]-True_value[2],result[1,3,]-True_value[3],result[1,4,]-True_value[4],result[1,5,]-True_value[5],result[1,6,]-True_value[6],result[1,7,]-True_value[7],result[1,8,]-True_value[8],result[1,9,]-True_value[9],
        names = t, 
        main = 'Bias when N=10^2',
        xlab = 't',
        ylab = 'bias',
        col = 'grey')
boxplot(result[2,1,]-True_value[1],result[2,2,]-True_value[2],result[2,3,]-True_value[3],result[2,4,]-True_value[4],result[2,5,]-True_value[5],result[2,6,]-True_value[6],result[2,7,]-True_value[7],result[2,8,]-True_value[8],result[2,9,]-True_value[9],
        names = t, 
        main = 'Bias when N=10^3',
        xlab = 't',
        ylab = 'bias',
        col = 'grey')
boxplot(result[3,1,]-True_value[1],result[3,2,]-True_value[2],result[3,3,]-True_value[3],result[3,4,]-True_value[4],result[3,5,]-True_value[5],result[3,6,]-True_value[6],result[3,7,]-True_value[7],result[3,8,]-True_value[8],result[3,9,]-True_value[9],
        names = t, 
        main = 'Bias when N=10^4',
        xlab = 't',
        ylab = 'bias',
        col = 'grey')
```